\documentclass[a4paper,11pt]{article}
\usepackage[hidelinks]{hyperref}
\usepackage[empty]{fullpage}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{latexsym}
\usepackage{ragged2e}
\usepackage{xcolor}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{
	left=1.4cm,
	top=0.8cm,
	right=1.2cm,
	bottom=1cm
}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}
\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]
%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
}
\newcommand{\resumePOR}[3]{
	\vspace{0.5mm}\item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}}
	\end{tabular*}
	\vspace{-2mm}
}
\newcommand{\resumeSubheading}[4]{
	\vspace{0.5mm}\item \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{\footnotesize{#4}} \\
		\textit{\footnotesize{#3}} &  \footnotesize{#2}\\
	\end{tabular*}
	\vspace{-2.4mm}
}
\newcommand{\resumeProject}[4]{
	\vspace{0.5mm}\item \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{\footnotesize{#3}} \\
		\footnotesize{\textit{#2}} & \footnotesize{#4}
	\end{tabular*}
	\vspace{-2.4mm}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{
	\resumeSubHeadingListStart
}{
	\begin{itemize}[leftmargin=*,labelsep=0mm]
}
\newcommand{
	\resumeHeadingSkillStart
}{
	\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]
}
\newcommand{
	\resumeItemListStart
}{
	\begin{justify}
		\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small
			}
			\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
		\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
		\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
	\vspace{2mm}
	\begin{tcolorbox}
		\textbf{\large #1}
	\end{tcolorbox}
	\vspace{-4mm}
}
\newcommand{\rightbox}[2]{
	\raisebox{0.0\height}{\footnotesize #1} #2
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}% 
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{
	MSc. Giovanni Gamaliel L칩pez Padilla
}
\newcommand{\course}{
	Computer Science and Engineering
}
\newcommand{\phone}{
	8712783770
}
\newcommand{\emaila}{
	giovannilopez9808@gmail.com
}

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------
\begin{tabularx}{\linewidth}{Lr}                                                                                      \\
	\textbf{\Large \name}                                      & \rightbox{\faEnvelope}{\emaila}          \\
	Master of Science in Computer Science and Machine Learning & \rightbox{\faPhone}{+52-\phone}          \\
	Bachelor in Physics with specialization in solar radiation & \rightbox{\faLinkedin}{LinkedIn Profile} \\
	Independent scientific researcher                          & \rightbox{\faGithub}{GitHub Profile}     \\
\end{tabularx}

%-----------EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeSubheading{
	Bachelor of Physics
}{
	Professional ID: xx
}{
	Universidad Autonoma de Nuevo Le칩n
}{
	2016-2020
}
\resumeSubheading{
	Master of Science with specialization in Computer Science and Industrial Mathematics
}{
}{
	Centro de Investigaci칩n en Matem치ticas
}{
	2021-2023
}
\resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
\resumeProject{
	Daily UV Index forecast based on in situ measurements in the Monterrey Metropolitan Area.
}{
	A website based facial authentication system, implemented using a Chrome Extension.
}{
}

\resumeItemListStart
\item Facilitating users' logins to websites without having to remember their credentials
\item Used Live detection techniques to create high order security.
\item Technology Used: Python, Reactjs, Bootstrap.
\resumeItemListEnd
\vspace{-2mm}

\resumeProject{
	Segmentation of the capillary vessels of the eyes using the pix2pix model.
}{
	Segmentation of the capillary vessels of the eyes using the pix2pix model.
}{
}

\resumeItemListStart
\item Used Firebase Authentication(SDK) to facilitate authentication \& Cloud Firestore to store data.
\item Technology Used: Reactjs, Firebase, Bootstrap, HTML.
\resumeItemListEnd
\vspace{-2mm}

\resumeProject{
	Automatic detection of aggressive tweets
}{
	Daily and weekly updated statistics tracking the number of COVID-19 cases, recovered, and deaths.
}{
}

\resumeItemListStart
\item Tracking world-wide cases using google maps and live API stats and datasets.
\item Technology Used : JavaScript , CSS, HTML, API.
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-8.5mm}


%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart
\resumeSubheading
{AWS Cloud Virtual Internship}{Online}
{AICTE-Eduskills}{May - July 2023}
\vspace{-2.0mm}
\resumeItemListStart
\item {In-depth understanding of AWS cloud computing services, including EC2, S3, RDS, Lambda, IAM, VPC, and more.}
\item {Proficient in designing, deploying, and managing fault-tolerant, highly available, and scalable AWS solutions.}
\item {Strong knowledge of architectural best practices, such as AWS Well-Architected Framework, security, performance, and cost optimization.}
\item {Hands-on experience in cloud infrastructure provisioning, monitoring, and automation using AWS Management Console and AWS CLI.}
\resumeItemListEnd

\vspace{-3.0mm}

\resumeSubheading
{Palo Alto Cybersecurity Virtual Internship}{Online}
{AICTE-Eduskills}{Dec 2022 - Feb 2023}
\vspace{-2.0mm}
\resumeItemListStart
\item {Learned the fundamentals of Security Operations Center (SOC).}
\item {Learned basics of Network \& Cloud Security.}
\resumeItemListEnd

\vspace{-3.0mm}

\resumeSubHeadingListEnd
\vspace{-5.5mm}







%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
\begin{itemize}[leftmargin=0.05in, label={}]
	\small{\item{
		            \textbf{Languages}{: C/C++, Python, Javascript, HTML+CSS } \\
		            \textbf{Libraries }{: C++ STL, Python Libraries, ReactJs }\\
		            \textbf{Web Dev Tools}{: Nodejs, VScode, Git, Github } \\
		            \textbf{Frameworks}{: ReactJs } \\
		            \textbf{Cloud/Databases}{:MongoDb, Firebase, Relational Database(mySql) } \\

		            \textbf{Relevent Coursework}{: Data Structures \& Algorithms, Operating Systems, Object Oriented Programming, Database Management System, Software Engineering. } \\
		            \textbf{Areas of Interest}{: Web Design and Development, Cloud Security.} \\
		            \textbf{Soft Skills}{: Problem Solving, Self-learning, Presentation, Adaptability} \\
		      }}
\end{itemize}
\vspace{-16pt}



%-----------Positions of Responsibility-----------------
\section{\textbf{Positions of Responsibility}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{On Desk Registrations Volunteer } % Position
{Aarhant Cyber Week Event - RCOEM, Nagpur} %Club,Event
{Oct - Dec 2022} %Tenure Period \\
\resumeItemListStart
\item {Helped to attract close to 300 attendees to the event.}
\item {Collected over Rs. 20,000 in entry fees for different activities.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5mm}




% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year

% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}



%-------------------------------------------
\end{document}
